Data preparation

### 2024-02-26 procesamiento/02-prod_prep-macro.Rmd
ajustes medidas desigualdad y homogeneidad

wid_df$ccode <- countrycode::countrycode(sourcevar = wid_df$country,origin = "iso2c",destination = "iso3n")
wid_df <- wid_df %>% filter(year==2018)%>% dplyr::select(ccode,wid_sharetop10,wid_rp90p50,wid_rd10d01,wid_sd10d01,wid_gini_disp)

cor(wid_df)
```

@@

```{r merge}
macro_data <- 
  left_join(wiid_2017,solt_2017) %>%
  left_join(pen_2017) %>% 
  left_join(otero) %>%
  left_join(ocde) %>% 
  left_join(wid_df)

@@

```{r}
df2 %>% 
  select(country3,wid_rd10d01,d10d1) %>%
  group_by(country3) %>% 
  summarise(wid_rd10d01=mean(wid_rd10d01), d10d1=mean(d10d1)) %>% View
```

>>>>

wid_df$ccode <- countrycode::countrycode(sourcevar = wid_df$country,origin = "iso2c",destination = "iso3n")

summary(wid_df)
wid_df_fill<- 
wid_df %>%
  group_by(country) %>% 
  fill(wid_p90p10, .direction = "up") %>%
  fill(wid_sp90p10, .direction = "up") %>%
  fill(wid_gini_disp, .direction = "up")
summary(wid_df_fill)

wid_df1 <- wid_df_fill %>% filter(year==2017) %>% select(ccode,starts_with("wid_"))
wid_df1$country <- NULL
sjPlot::tab_corr(wid_df1)
```

@@

```{r merge}
macro_data <- 
  left_join(wiid_2017,solt_2017) %>%
  left_join(pen_2017) %>% 
  left_join(otero) %>%
  left_join(ocde) %>% 
  left_join(wid_df1)

@@
